### 2014-01-16 Docs/visualization/visualization.tex
hyperrefs
more yt stuff

{\tt plotsinglevar.py} does visualizations of 2-d \boxlib\ plotfiles,
and slices through 3-d \boxlib\ plotfiles.  A simple plot can be made
via:
\begin{verbatim}
plotsinglevar.py --log -o test.png plt00000/ tfromp
\end{verbatim}
This will make a plot of ``tfromp'' from the plotfile {\tt plt00000} with log scaling,
and store the output in {\tt test.png}.  See Figure~\ref{fig:python}.
If you don't do `{\tt -o}', then a default output filename consisting of the
plotfile name + component will be used.

@@

\subsection{Installing \yt}
The easiest way to obtain \yt is through the use of an installation script:
\begin{lstlisting}[language=bash,mathescape=false]
> wget http://hg.enzotools.org/yt/raw-file/stable/doc/install_script.sh
> bash install_script.sh
\end{lstlisting}
By default, this \yt install script will download and install, in its
own isolated environment, all the secondary utilities needed to get
\yt up and running.  Note that this currently includes installing {\it
  hdf5, zlib, bzip2, libpng, freetype, python, numpy, matplotlib,
  mercurial, ipython, h5py, Cython, Forthon} as well as a \yt {\it
  mercurial} bundle of changes.  You can turn off the automatic
installation of any of these particular packages by setting the
appropriate {\tt INST\_}* variable to zero in the install script; you
may have to then change some of *{\tt \_DIR} variables to point to
your own particular installation of that package.  It is usually best
to just let \yt install its own stuff, which ensures things are
working properly.

@@

In [1]: 
\end{lstlisting}
Codes like {\tt Enzo} use what are called {\it parameter files} to
describe the general information---number of levels, domain
dimensions, time, etc.---of a a dataset.  \yt likes to grab this
information before working on any specific data; this is accomplished
via the convenience method \textcolor{blue}{\tt load}:
\begin{lstlisting}[language=Python]
In [1]: pf = load(``plt00166'')
\end{lstlisting}
This method returns an instance of the {\tt StaticOutput} class.  One
of the easiest ways of handling plots is via a {\tt PlotCollection}
object
\begin{lstlisting}[language=Python]
In [2]: center = (pf.domain_right_edge + pf.domain_left_edge) / 2.0
In [3]: pc = PlotCollection(pf,center)
\end{lstlisting}
By default, the {\tt PlotCollection} constructor places the center of
the plot to be at the location of peak density.  Here we have
calculated the center of the domain by accessing the lower and upper
domain boundaries via the {\tt numpy} arrays {\tt
  pf.domain\_left\_edge} and {\tt pf.domain\_right\_edge},
respectively.  Note that up until this point, \yt has not actually
loaded the AMR dataset.

Now we would like to take some slices of tfromp in the dataset and
generate some 2-d plots.  To do this, we will use the {\tt
  PlotCollection}'s \textcolor{blue}{\tt add\_slice} method:
\begin{lstlisting}[language=Python]
In [4]: pc.add_slice(``tfromp'',0)
In [5]: pc.add_slice(``tfromp'',1)
In [6]: pc.add_slice(``tfromp'',2)
\end{lstlisting}
The first call to \textcolor{blue}{\tt add\_slice} builds an {\tt
  AMRHierarchy} object associated with {\tt pf}.  The {\tt
  AMRHierarchy} object contains information about the actual dataset,
such as its layout in the simulation domain or on disk.  Building the
hierarchy is expensive, but once it is built the data it contains can
be accessed via attributes and dictionary lookup.  In other words, the
subsequent \textcolor{blue}{\tt add\_slice} operations are relatively
cheap.  The first parameter to the \textcolor{blue}{\tt add\_slice}
method is obviously the variable we want; the second (optional)
parameter specifies an coordinate axis orthogonal to the slice being
made---0 for x, 1 for y, 2 for z.  Now we want to save the plots from
the {\tt PlotCollection}; this is done with the \textcolor{blue}{\tt
  save} method, which takes an optional basename for the generated files:
\begin{lstlisting}[language=Python]
In [7]: pc.save(``my_cool_images'')
\end{lstlisting}
This generates the following image files:
\begin{lstlisting}[language=Python]
Out[7]: 
['my_cool_images_Slice_x_tfromp.png',
 'my_cool_images_Slice_y_tfromp.png',
 'my_cool_images_Slice_z_tfromp.png']
\end{lstlisting}
Figure \ref{fig:yt_slice} shows an example of one of the slice images.
Note that this was a quick and dirty generation of the image---there
is a lot of space around the figure, which can be removed with various
options to the \yt methods.  Also, the user can specify derived
variables, log-scaling, annotations, etc. For more information see the
documentation at {\tt http://yt.enzotools.org/doc/}.

@@

# the plotfile I'm interested in
fn = ``plt00166''

@@

# add some slices of tfromp
pc.add_slice(``tfromp'',0)
pc.add_slice(``tfromp'',1)
pc.add_slice(``tfromp'',2)

# save our plots to a files with basename
# ``my_cool_images''
pc.save(``my_cool_images'')
\end{lstlisting}

>>>>

{\tt plotsinglevar.py} does visualizations of 2-d \boxlib\ plotfiles,
and slices through 3-d \boxlib\ plotfiles.  A simple plot can be made
via:
\begin{verbatim}
plotsinglevar.py --log -o test.png plt00000/ tfromp
\end{verbatim}
This will make a plot of ``{\tt tfromp}'' from the plotfile {\tt plt00000} with log scaling,
and store the output in {\tt test.png}.  See Figure~\ref{fig:python}.
If you don't do `{\tt -o}', then a default output filename consisting of the
plotfile name + component will be used.

@@

\subsection{Installing \yt}
The easiest way to obtain \yt is through the use of an installation script:
\begin{lstlisting}[language=bash,mathescape=false]
> wget http://hg.yt-project.org/yt/raw/yt-3.0/doc/install_script.sh
> bash install_script.sh
\end{lstlisting}
By default, this \yt install script will download and install, in its
own isolated environment, all the secondary utilities needed to get
\yt up and running.  Note that this currently includes installing {\it
  hdf5, zlib, bzip2, libpng, freetype, python, numpy, matplotlib,
  mercurial, ipython, h5py, Cython, Forthon} as well as a \yt {\it
  mercurial} bundle of changes.  You can turn off the automatic
installation of any of these particular packages by setting the
appropriate {\tt INST\_}* variable to zero in the install script; you
may have to then change some of *{\tt \_DIR} variables to point to
your own particular installation of that package.  It is usually best
to just let \yt install its own stuff, which ensures things are
working properly.

@@

In [1]: 
\end{lstlisting}
Codes like {\tt Enzo} use what are called {\it parameter files} to
describe the general information---number of levels, domain
dimensions, time, etc.---of a a dataset.  \yt likes to grab this
information before working on any specific data; this is accomplished
via the convenience method \textcolor{blue}{\tt load}:
\begin{lstlisting}[language=Python]
In [1]: pf = load("plt00166")
\end{lstlisting}
Note that some older versions of \yt needed an {\tt inputs} file 
in the same directory as the plotfile, but as of \yt 3.0, all the
necessary metadata is obtained from the {\tt job\_info} file inside
the plotfile directory.
The {\tt load} method returns an instance of the {\tt StaticOutput} class.  One
of the easiest ways of handling plots is via a {\tt PlotCollection}
object
\begin{lstlisting}[language=Python]
In [2]: center = (pf.domain_right_edge + pf.domain_left_edge) / 2.0
In [3]: pc = PlotCollection(pf,center)
\end{lstlisting}
By default, the {\tt PlotCollection} constructor places the center of
the plot to be at the location of peak density.  Here we have
calculated the center of the domain by accessing the lower and upper
domain boundaries via the {\tt numpy} arrays {\tt
  pf.domain\_left\_edge} and {\tt pf.domain\_right\_edge},
respectively.  Note that up until this point, \yt has not actually
loaded the AMR dataset.

Now we would like to take some slices of tfromp in the dataset and
generate some 2-d plots.  To do this, we will use the {\tt
  PlotCollection}'s \textcolor{blue}{\tt add\_slice} method:
\begin{lstlisting}[language=Python]
In [4]: pc.add_slice("tfromp",0)
In [5]: pc.add_slice("tfromp",1)
In [6]: pc.add_slice("tfromp",2)
\end{lstlisting}
The first call to \textcolor{blue}{\tt add\_slice} builds an {\tt
  AMRHierarchy} object associated with {\tt pf}.  The {\tt
  AMRHierarchy} object contains information about the actual dataset,
such as its layout in the simulation domain or on disk.  Building the
hierarchy is expensive, but once it is built the data it contains can
be accessed via attributes and dictionary lookup.  In other words, the
subsequent \textcolor{blue}{\tt add\_slice} operations are relatively
cheap.  The first parameter to the \textcolor{blue}{\tt add\_slice}
method is obviously the variable we want; the second (optional)
parameter specifies an coordinate axis orthogonal to the slice being
made---0 for x, 1 for y, 2 for z.  Now we want to save the plots from
the {\tt PlotCollection}; this is done with the \textcolor{blue}{\tt
  save} method, which takes an optional basename for the generated files:
\begin{lstlisting}[language=Python]
In [7]: pc.save("my_cool_images")
\end{lstlisting}
This generates the following image files:
\begin{lstlisting}[language=Python]
Out[7]: 
['my_cool_images_Slice_x_tfromp.png',
 'my_cool_images_Slice_y_tfromp.png',
 'my_cool_images_Slice_z_tfromp.png']
\end{lstlisting}
Figure \ref{fig:yt_slice} shows an example of one of the slice images.
Note that this was a quick and dirty generation of the image---there
is a lot of space around the figure, which can be removed with various
options to the \yt methods.  Also, the user can specify derived
variables, log-scaling, annotations, etc. For more information see the
documentation at \url{http://yt-project.org/docs/dev/}\, .

@@

# the plotfile I'm interested in
fn = "plt00166"

@@

# add some slices of tfromp
pc.add_slice("tfromp",0)
pc.add_slice("tfromp",1)
pc.add_slice("tfromp",2)

# save our plots to a files with basename
# "my_cool_images"
pc.save("my_cool_images")
\end{lstlisting}
